Siderius, D.~W. and Shen, V.~K. On Adsorption Hysteresis in Closed-end Pores:\\ Isotherm Reconstruction and Free Energy Analysis via Flat-histogram Monte Carlo Simulation. 2016 International Conference on Fundamentals of Adsorption, Friedrichshafen, Germany, June 2016.

Siderius, D.~W., Espinal, L., Johnson, R.~D., and van Zee, R.~D. NIST Infrastructure for Cataloging and Curating Adsorbent Materials, Data, and Properties. 2013 International Conference on Fundamentals of Adsorption, Baltimore, Maryland, May 2013.

Espinal, L., Siderius, D.~W., Johnson, R.~D., and Southon, P. Preliminary Inter-Laboratory Comparison of High-Pressure Gas Sorption Data. 2013 International Conference on Fundamentals of Adsorption, Baltimore, Maryland, May 2013.

Espinal L., Wong-Ng, W., Allen, A.~J., Snyder, C.~R., Chiu, C., Siderius, D.~W., Li, L., Cockayne, E., Espinal, A.~E., and Suib, S.~L. Time dependent CO$_2$ sorption hysteresis by octahedral molecular sieves with manganese oxide framework. Gordon Conference on Nanoporous Materials and Their Applications, Holderness School, New Hampshire, August 2011.

Krekelberg, W.~P., Siderius, D.~W., Errington, J.~R., Truskett, T.~M., and Shen, V.~K. Correlations between static thermodynamic properties and dynamic transport properties of confined fluids: application to adsorption and diffusion in porous solids and rough materials. Ninth International Symposium on the Characterisation of Porous Solids, Dresden, Germany, June 2011.

Siderius, D.~W., Krekelberg, W.~P., and Shen, V.~K. Use of the Transition-Matrix Monte Carlo simulation method to study metastability and phase transitions in gas adsorption processes. Ninth International Symposium on the Characterisation of Porous Solids, Dresden, Germany, June 2011.

Siderius, D.~W. and Gelb, L.~D. Advanced Computational Techniques for Modeling Light Gas Adsorption in Complex Porous Materials: High-Performance Implementation of Lattice-Gas Density Functional Theory. 2010 International Conference on Fundamentals of Adsorption, Awaji, Japan, May 2010.

Corti, D.~S., Siderius, D.~W., Uline, M.~J., and Sturtevant, B.~W. Molecular Modeling of Liquids and Complex Fluids. 2006 Graduate Student Colloquium, School of Chemical Engineering, Purdue University, March 2006.

Siderius, D.~W. and Corti, D.~S. Thermodynamically Consistent Adaptation of Scaled Particle Theory to an Arbitrary Equation of State: Hard Sphere Fluid Properties and a New Reference System for Solvation Theories. 2005 American Institute of Chemical Engineers Annual Meeting, Cincinnati, Ohio.

Siderius, D.~W. and Corti, D.~S. Origin of Depletion Forces Described via a Scaled Particle Theory Integral Equation, 2005 Graduate Research Symposium, School of Chemical Engineering, Purdue University, August 2005.

Siderius, D.~W. and Corti, D.~S. Entropic Force between a Colloidal Particle and a Wall: Calculation via a new Scaled Particle Theory of Inhomogeneous Fluids, 2004 Graduate Research Symposium, School of Chemical Engineering, Purdue University, August 2004.

Siderius, D.~W. and Corti, D.~S. Entropic Control of Colloidal Dispersions: Scaled Particle Theory of Hard Spheres near a Wall. 2004 Graduate Student Colloquium, School of Chemical Engineering, Purdue University, March 2004.
