{\it Siderius, D.~W.}, Mahynskik, N.~A., and Shen, V.~K. Calculation of the Isosteric Enthalpy of Adsorption in Monte Carlo Molecular Simulation: New Equations Addressing Bulk Phase Nonideality and Isosteres of Total Adsorption. 2017 AIChE Annual Meeting, Minneapolis, Minnesota.

{\it Siderius, D.~W.}, Shen, V.~K., Johnson, R.~D., and van Zee, R.~D. NIST Data Resources for Adsorption. 2017 International Symposium on the Characterization of Porous Solids, Avignon, France.

Hatch, H.~W., Krekelberg, W.~P., Mountain, R.~M., Shen, V.~K., and {\it Siderius, D.~W.}. The NIST Standard Reference Simulation Website: Reference Calculations and Evaluated Thermodynamics Properties to Aid Molecular Simulation Users. 2016 AIChE Annual Meeting, San Francisco, California.

Mahynski, N.~A., {\it Siderius, D.~W.}, and Shen, V.~K. Exploring the Link Between the Properties of Flexible, MOF-like Adsorbent Materials and Adsorption Behavior Via Flat-Histogram Monte Carlo. 2016 AIChE Annual Meeting, San Francisco, California.

{\it Siderius, D.~W.}, Shen, V.~K., Johnson, R.~D., and van Zee, R.~D. The NIST/ARPA-E Database of Novel and Emerging Adsorbent Materials. 2016 International Conference on Fundamentals of Adsorption, Friedrichshafen, Germany.

{\it Siderius, D.~W.}, Shen, V.~K., and Do, D.~D. On Adsorption Hysteresis in Closed-end Pores: Isotherm Reconstruction and Free Energy Analysis via Flat-histogram Monte Carlo Simulation. 2015 AIChE Annual Meeting, Salt Lake City, Utah.

{\it Gor, G.~Y.}, Siderius, D.~W. Rasmussen, C.~J., Krekelberg, W.~P., Shen, V.~K., and Bernstein, N.~B. Extracting Information about Pore Sizes from Ultrasonic Experiments. 2015 AIChE Annual Meeting, Salt Lake City, Utah.

{\it Krekelberg, W.~P.}, Siderius, D.~W., Truskett, T.~M., Errington, J., and Shen, V.~K. Correlations between static thermodynamic properties and dynamic transport properties of confined fluids: Application to adsorption and diffusion in porous solids. 2015 NIST Thermophysical Properties Symposium, Boulder, Colorado.

{\it Siderius, D.~W.}, Shen, V.~K., Johnson, R.~D., and van Zee, R.~D. The NIST/ARPA-E Database of Novel and Emerging Adsorbent Materials. 2015 NIST Thermophysical Properties Symposium, Boulder, Colorado.

Shen, V.~K. and {\it Siderius, D.~W.} Molecular Simulation Study of Adsorption in Compliant Porous Materials. 2015 NIST Thermophysical Properties Symposium, Boulder, Colorado.

{\it Siderius, D.~W.}, Shen, V.~K., and Do, D.~D. On Adsorption Hysteresis in Closed-end Pores: Isotherm Reconstruction and Free Energy Analysis via Flat-histogram Monte Carlo Simulation. 2015 NIST Thermophysical Properties Symposium, Boulder, Colorado.

{\it Siderius, D.~W.}, Shen, V.~K., Johnson, R.~D., and van Zee, R.~D. The NIST/ARPA-E Database of Novel and Emerging Adsorbent Materials. 2015 International Workshop on the Characterization of Porous Materials, Delray Beach, Florida.

{\it Krekelberg, W.~P.}, Siderius, D.~W., Truskett, T.~M., Errington, J., and Shen, V.~K. Correlations between static thermodynamic properties and dynamic transport properties of confined fluids: Application to adsorption and diffusion in porous solids. 2015 International Workshop on the Characterization of Porous Materials, Delray Beach, Florida.

{\it Siderius, D.~W.}, Shen, V.~K., Johnson, R.~D., and van Zee, R.~D., The NIST/ARPA-E Database of Novel and Emerging Adsorbent Materials. 2014. Workshop on Measurement Needs in the Adsorption Sciences, Gaithersburg, Maryland.

Shen, V.~K. and {\it Siderius, D.~W.}, Exploration of the Relationship between Bare Sorbent Flexibility and Resulting Adsorption Behavior via Flat-histogram Monte Carlo.
2014 American Institute of Chemical Engineers Annual Meeting, Atlanta, Georgia.

Shen, V.~K. and {\it Siderius, D.~W.}, Interrogating Simple Pore Models Using Flat-Histogram Sampling Methods to Understand the Effect of Sorbent Flexibility On Fluid Adsorption. 2014 NIST Workshop on Atomistic Simulations for Industrial Needs, Gaithersburg, Maryland. (Plenary)

Shen, V.~K. and {\it Siderius, D.~W.}, Interrogating Simple Pore Models Using Flat-Histogram Sampling Methods to Understand the Effect of Sorbent Flexibility On Fluid Adsorption. 2014 International Symposium on the Characterization of Porous Solids, Granada, Spain.

Shen, V.~K. and {\it Siderius, D.~W.}, Interrogating Simple Pore Models Using Flat-Histogram Sampling Methods to Understand the Effect of Sorbent Flexibility On Fluid Adsorption. 2013 American Institute of Chemical Engineers Annual Meeting, San Francisco, California.

{\it Siderius, D.~W.}, A Materials Simulation Challenge: Why, What, and How? 2013 NIST Workshop on Atomistic Simulations for Industrial Needs, Gaithersburg, Maryland.

{\it Siderius, D.~W.}, Krekelberg, W.~P., and Shen, V.~K. Use of the Transition Matrix Monte Carlo Simulation Method to Study Metastability and Phase Transitions In Gas Adsorption Processes. 2013 International Conference on Fundamentals of Adsorption, Baltimore, Maryland. (Invited)

{\it Espinal, L.}, Wong-Ng, W., Allen, A.~J., Snyder, C.~R., Siderius, D.~W., Chiu, C, Espinal, A.~E., and Suib, S.~L. Time Dependent CO2 Sorption Hysteresis by Octahedral Molecular Sieves with Manganese Oxide Framework. 2013 International Conference on Fundamentals of Adsorption, Baltimore, Maryland.

{\it Siderius, D.~W.}, Fagan, J.~A., and Shen, V.~K. Thermophysical and Structural Properties of Electrolyte Solutions Confined in a Carbon Nanotube. 2012 American Institute of Chemical Engineers Annual Meeting, Pittsburgh, Pennsylvania.

{\it Siderius, D.~W.}, Krekelberg, W.~P., and Shen, V.~K. Use of the Transition Matrix Monte Carlo Simulation Method to Study Metastability and Phase Transitions In Gas Adsorption Processes. 2012 NIST Thermophysical Properties Symposium, Boulder, Colorado.

Espinal, L., Wong-Ng, W., Allen, A.~J., Snyder, C.~R., {\it Siderius, D.~W.}, Chiu, C, Espinal, A.~E., and Suib, S.~L. Time Dependent CO2 Sorption Hysteresis by Octahedral Molecular Sieves with Manganese Oxide Framework. 2012 International Workshop on the Characterization of Porous Materials, Delray Beach, Florida.

{\it Siderius, D.~W.}, Krekelberg, W.~P., and Shen, V.~K. Use of the Transition Matrix Monte Carlo Simulation Method to Study Metastability and Phase Transitions In Gas Adsorption Processes. 2011 American Institute of Chemical Engineers Annual Meeting, Minneapolis, Minnesota.

{\it Espinal, L.}, Wong-Ng, W., Allen, A.~J., Snyder, C.~R., Siderius, D.~W., Chiu, C, Espinal, A.~E., and Suib, S.~L. Time Dependent CO2 Sorption Hysteresis by Octahedral Molecular Sieves with Manganese Oxide Framework. 2011 American Institute of Chemical Engineers Annual Meeting, Minneapolis, Minnesota.

{\it Siderius, D.~W.}, Krekelberg, W.~P., Roberts, C.~J., and Shen, V.~K. Osmotic Virial Coefficients of Protein Solutions: Effect of Differing Ensemble Constraints and Connection to Experiment. 2010 American Institute of Chemical Engineers Annual Meeting, Salt Lake City, Utah.

{\it Krekelberg, W.~P.}, Siderius, D.~W., Truskett, T.~M., Errington, J., and Shen, V.~K. How Surface Features and Roughness Impact the Structure, Dynamics, and Thermodynamics of a Confined Fluid. 2010 American Institute of Chemical Engineers Annual Meeting, Salt Lake City, Utah.

{\it Barnes, B.~C.}, Siderius, D.~W., and Gelb, L.~D. Structure and Thermodynamics of Polyomino Fluids and Crystals. 2010 Midwest Thermodynamics and Statistical Mechanics Conference, Notre Dame, Indiana.

{\it Siderius, D.~W.} and Gelb, L.~D. Modeling Adsorption in Complex Structures: Use of Finely-Discretized Lattice-Gas DFT to Study the Effects of Pore Shape and Surface Roughness On Adsorption of Simple Gases. 2010 International Conference on Fundamentals of Adsorption, Awaji, Japan.

{\it Siderius, D.~W.} and Gelb, L.~D.  Characterization of Microporous Adsorbents: A Study of the Concept of ``Surface Area'' of Metal-Organic Frameworks. 2009 American Institute of Chemical Engineers Annual Meeting, Nashville, Tennessee.

{\it Siderius, D.~W.} and Gelb, L.~D. Modeling Adsorption in Complex Structures: Use of Finely-Discretized Lattice-Gas DFT to Study the Effects of Pore Length, Shape, and Surface Roughness On Adsorption of Simple Gases. 2009 American Institute of Chemical Engineers Annual Meeting, Nashville, Tennessee. 

Barnes, B.~C., Siderius, D.~W., and {\it Gelb, L.~D.}  Structure, Thermodynamics, and Solubility in Polyomino Fluids. 2009 American Institute of Chemical Engineers Annual Meeting, Nashville, Tennessee.

{\it Siderius, D.~W.} and Gelb, L.~D. Modeling Adsorption in Complex Structures: Use of a Recent Lattice-Gas DFT to Study the Effect of Pore Length, Shape, and Surface Roughness on Adsorption of Simple Gases. 2009 International Workshop on the Characterization of Porous Materials, New Brunswick, New Jersey.

{\it Siderius, D.~W.} and Gelb, L.~D. A high-resolution lattice model for adsorption: {W}eighted density functional theory for lattice fluids and application to adsorption in porous materials. 2008 American Institute of Chemical Engineers Annual Meeting, Philadelphia, Pennsylvania.

{\it Barnes, B.C.}, Siderius, D.~W., and Gelb, L.~D. Monte carlo simulation of tetronimoes: {S}tructural and thermodynamic properties of a seven-component on-lattice fluid model. 2008 American Institute of Chemical Engineers Annual Meeting, Philadelphia, Pennsylvania.

{\it Siderius, D.~W.} and Gelb, L.~D. Improved lattice models for adsorption: Application to characterization and capillary phenomena. 2008 International Symposium on the Characterisation of Porous Solids, Edinburgh, United Kingdom.

{\it Siderius, D.~W.} and Corti, D.~S. Extension Of Gibbs' Dividing Surface Analysis To Cavities That Intersect A Planar Surface: Calculation Of The Line Tension Of The Hard-Sphere Fluid. 2007 American Institute of Chemical Engineers Annual Meeting, Salt Lake City, Utah.

{\it Uline, M.~J.}, Siderius, D.~W. and Corti, D.~S. On the Apparent Breakdown of Equipartition in Molecular Dynamics Ensembles Applied to Nanoscale Systems. 2007 American Institute of Chemical Engineers Annual Meeting, Salt Lake City, Utah.

{\it Siderius, D.~W.} and Corti, D.~S. Geometric Model of Depletion Forces in Hard-Sphere Colloidal Dispersions Exposed to Various Surfaces. 2006 American Institute of Chemical Engineers Annual Meeting, San Francisco, California.

{\it Siderius, D.~W.} and Corti, D.~S. On the Use of Scaled Particle Theory to Determine a Broad Range of Hard-Sphere Fluid Properties with High Accuracy. 2006 American Institute of Chemical Engineers Annual Meeting, San Francisco, California.

{\it Siderius, D.~W.} Corti, D.~S. Geometric Model of Depletion Forces in Hard-Sphere Colloidal Dispersions Exposed to Various Surfaces. 2006 American Chemical Society Colloid and Surface Science Symposium, Boulder, Colorado.

{\it Siderius, D.~W.} and Corti, D.~S. Geometric Model of Depletion Forces in Hard-Sphere Colloidal Dispersions Exposed to Various Surfaces. 2006 Midwest Thermodynamics and Statistical Mechanics Conference, Akron, Ohio.

{\it Siderius, D.~W.} and Corti, D.~S. Investigation of Role of Geometry and Fluid Structure in the Description of Depletion Forces via Scaled Particle Theory-based Integral Equations for Hard Sphere Fluids. 2005 American Institute of Chemical Engineers Annual Meeting, Cincinnati, Ohio.

{\it Siderius, D.~W.} and Corti, D.~S. Investigation of Role of Geometry and Fluid Structure in the Description of Depletion Forces via Scaled Particle Theory-based Integral Equations for Hard Sphere Fluids. 2005 American Chemical Society Colloid and Surface Science Symposium, Potsdam, New York.

{\it Siderius, D.~W.} and Corti, D.~S. Investigation of Role of Geometry and Fluid Structure in the Description of Depletion Forces via Scaled Particle Theory-based Integral Equations for Hard Sphere Fluids. 2005 Midwest Thermodynamics and Statistical Mechanics Conference, West Lafayette, Indiana.

{\it Siderius, D.~W.} and Corti, D.~S. Depletion Forces From a New Scaled Particle Theory of Inhomogeneous Hard Particle Fluids. 2004 American Institute of Chemical Engineers Annual Meeting, Austin, Texas.

Siderius, D.~W. and {\it Corti, D.~S.} The Entropic Force between a Colloidal Particle and a Wall: A New Determination Based on Extension of Scaled Particle Theory to Inhomogeneous Fluids. 2004 American Chemical Society Colloid and Surface Science Symposium, New Haven, Connecticut.

{\it Siderius, D.~W.} and Corti, D.~S. Depletion Forces from a New Scaled Particle Theory of Hard Particle Fluids. 2004 Midwest Thermodynamics and Statistical Mechanics Conference, Buffalo, New York.
