Wong-Ng, W., Williamson, I., Walker, M., Siderius, D.~W., Culp, J.~T., Chen, Y-S., and Li, L. Electronic Structure, Pore Size Distribution, and Sorption Characterization of an unusual MOF, {[Ni(dpbz)][Ni(CN)$_4$]}$_n$, dpbz=1,4-bis(4-pyridyl)benzene. 2018. {\it Powder Diffr.}, In Preparation.

Wong-Ng, W., Culp, J.~T., Siderius, D.~W., and Chen, Y-S. Synthesis and Synchrotron X-ray characterization of two 2D Hoffman related compounds [Ni(p-Xylylenediamine)$_n$Ni(CN)$_4$] and [Ni(p-tetrafluoroxylylenediamine)$_n$Ni(CN)$_4$]. 2018. {\it Solid State Sci.}, In Preparation.

Shen, V.~K., Siderius, D.~W., and Mahynski, N.~A. Molecular Simulation of Capillary Phase Transitions in Flexible Porous Materials. 2018. {\it J. Chem. Phys}, In Preparation.

Siderius, D.~W., Krekelberg, W.~P., Chiang, W-S., Shen, V.~K., and Liu, Y. Quasi-Two-dimensional Phase Transition of Methane Adsorbed in Cylindrical Silica Mesopores, {\it Langmuir}. 2017. In Press.

Krekelberg, W.~P., Siderius, D.~W., Shen, V.~K., Truskett, T.~M., and Errington, J.~R. Position-dependent dynamics explain pore-averaged diffusion in strongly attractive adsorptive systems. 2017. {\it Langmuir}, {\bf 33}, 13955.

Krekelberg, W.~P., Siderius, D.~W., Shen, V.~K., Truskett, T.~M., and Errington, J.~R. Connection Between Thermodynamics and Dynamics of Simple Fluids in Pores: Impact of Fluid−Fluid Interaction Range and Fluid−Solid Interaction Strength. 2017. {\it J. Phys. Chem. C}, {\bf 121}, 16316.

Siderius, D.~W., Mahynski, N.~A., and Shen, V.~K. Relationship between pore-size distribution and flexibility of adsorbent materials: statistical mechanics and future material characterization techniques. 2017. {\it Adsorption}, {\bf 23}, 593.

Gor, G.~Y., Siderius, D.~W., Shen, V.~K., and Bernstein, N.~B. Modulus--Pressure Equation for Confined Fluids. 2016, {\it J. Chem. Phys.}, {\bf 145}, 164505.

Schultz, N.~E., Riaz, A., Brennan, J.~K., Frankel, K.~A., Moore, J.~D., Moore, J.~D., Mountain, R.~D., Ross, R.~B., Thommes, M., Shen, V.~K., Siderius, D.~W., and Smith, K.~D. The Eighth Industrial Fluid Properties Simulation Challenge. 2016, {\it Adsorption Sci. Tech}, {\bf 34}, 3.

Ross, R.~B., Aeschliman, D.~B., Riaz, A., Brennan, J.~K., Brostrom, M.~L., Frankel, K.~A., Moore, J.~D., Moore, J.~D., Mountain, R.~D., Poiriera, D.~M., Thommes, M., Shen, V.~K., Schultz, N.~E., Siderius, D.~W., and Smith, K.~D. Adsorption, X-ray Diffraction, Photoelectron, and Atomic Emission Spectroscopy Benchmark Studies for the Eighth Industrial Fluid Properties Simulation Challenge. 2016, {\it Adsorption Sci. Tech}, {\bf 34}, 13.

Gor, G.~Y., Siderius, D.~W., Rasmussen, C.~J., Krekelberg, W.~P., Shen, V.~K., and Bernstein, N.~B. Relation between pore size and the compressibility of a confined fluid. 2015, {\it J. Chem. Phys.}, {\bf 143}, 194506.

Wong-Ng, W., Kaduk, J., Siderius, D.~W., Allen, A.~J., Espinal, L., Boyerinas, B.~M., Levin, I., Suchomel, M., Ilavsky, J., Li, L., Williamson, E., Cockayne, E., and Wu, H. Reference diffraction patterns, microstructure, and pore size distribution for the copper (II) benzene-1,3,5-tricarboxylate metal organic framework ({Cu-BTC}) compounds. 2015, {\it Powder Diffr.}, {\bf 30}, 2.

Shen, V.~K. and Siderius, D.~W. Elucidating the effects of sorbent flexibility on fluid adsorption using simple models and flat-histogram sampling methods. 2014, {\it J. Chem. Phys.}, {\bf 140}, 244106.

Ross, R.~.B., Ahmad, R., Brennan, J.~K., Frankel, K.~A., Moore, J.~D., Moore, J.~D., Mountain, R.~D., Shen, V.~K., Schultz, N.~E., Siderius, D.~W., Smith, K.~D., and Thommes, M. The Seventh Industrial Fluid Properties Simulation Challenge. 2014, {\it Fluid Phase Equil.}, {\bf 366}, 136.

Ross, R.~.B., Brennan, J.~K., Frankel, K.~A., Moore, J.~D., Moore, J.~D., Mountain, R.~D., Ahmad, R., Thommes, M., Shen, V.~K., Schultz, N.~E., Siderius, D.~W., and Smith, K.~D. Perfluorohexane Adsorption in BCR-704 Faujasite Zeolite Benchmark Studies for the Seventh Industrial Fluid Properties Simulation Challenge. 2014, {\it Fluid Phase Equil.}, {\bf 366}, 141.

Krekelberg, W.~P., Siderius, D.~W., Shen, V.~K., Errington, J.~R., and Truskett, T.~M. Connection between thermodynamics and dynamics of simple fluids in highly attractive pores, 2013, {\it Langmuir}, {\bf 29},  14527.

Wong-Ng, W., Culp, J.~T., Chen, Y.~S., Zavalij, P., Espinal, L., Siderius, D.~W., Allen, A.~J., Scheins, S. and Matranga, C. Improved Synthesis and Crystal Structure of the Flexible Pillared Layer Porous Coordination Polymer: Ni(1,2-bis(4-pyridyl)ethylene)[Ni(CN)4], 2013, {\it Cryst. Eng. Comm.}, {\bf 115}, 4684.

Siderius, D.~W. and Shen, V.~K. Use of the Grand Canonical Transition-Matrix Monte Carlo Method to Model Adsorption Hysteresis in Porous Materials, 2013. {\it J. Phys. Chem. C}, {\bf 117}, 5861.

Espinal, L., Wong-Ng, W., Allen, A.~J., Snyder, C.~R., Chiu, C., Bendersky, L.~A., Siderius, D.~W., Espinal, A.~E., and Suib, S.~L. Time dependent CO2 sorption hysteresis by octahedral molecular sieves with manganese oxide framework, 2012. {\it J. Am. Chem. Soc.}, {\bf 134}, 7944.

Siderius, D.~W., Krekelberg, W.~P., Roberts, C.~J., and Shen, V.~K. Osmotic virial coefficients for model protein and colloidal solutions: Importance of ensemble constraints, 2012. {\it J. Chem. Phys.}, {\bf 136}, 175102.

Siderius, D.~W. and Gelb, L.~D. Extension of the Steele 10-4-3 Potential for Adsorption Calculations in Cylindrical, Spherical, and Other Pore Geometries, 2011. {\it J. Chem. Phys.}, {\bf 135}, 084703.

Siderius, D.~W. and Corti, D.~S. Extension of scaled particle theory to inhomogeneous hard particle fluids. IV. Cavity growth at any distance relative to a planar hard wall. 2011. {\it Phys. Rev. E}, {\bf 83}, 031126.

Siderius, D.~W. and Corti, D.~S. On the line tension of curved boundary layers. I. Boundary thermodynamics. 2009. {\it J. Phys. Chem. B}, {\bf 113}, 13849 (Invited).

Siderius, D.~W. and Gelb, L.~D. Thermodynamic and structural properties of finely discretized on-lattice hard-sphere fluids: Virial coefficients, free energies, and direct correlation functions. 2009. {\it J. Chem. Phys.}, {\bf 131}, 084503.

Barnes, B.~C., Siderius, D.~W., and Gelb, L.~D. Structure, thermodynamics, and solubility in tetromino fluids. 2009. {\it Langmuir}, {\bf 25}, 6702.

Siderius, D.~W. and Gelb, L.~D. Predicting gas adsorption in complex microporous and mesoporous materials using a new density functional theory of finely-discretized lattice fluids. 2009. {\it Langmuir}, {\bf 25}, 1296.

Uline, M.~J., Siderius, D.~W. and Corti, D.~S. On the generalized equipartition theorem in molecular dynamics ensembles and the microcanonical statistical mechanics of small systems. 2008. {\it J. Chem. Phys.}, {\bf 128}, 124301.

Siderius, D.~W. and Corti, D.~S. On the use of multiple interpolation functions in scaled particle theory to improve the predictions of the properties of the hard-sphere fluid. 2007. {\it J. Chem. Phys.}, {\bf 127}, 144502.

Siderius, D.~W. and Corti, D.~S. Extension of scaled particle theory to inhomogeneous hard particle fluids. III. Entropic force exerted on a cavity that intersects a hard wall. 2007. {\it Phys. Rev. E}, {\bf 75}, 011108.

Siderius, D.~W. and Corti, D.~S. Thermodynamically consistent adaptation of scaled particle theory to an arbitrary hard sphere equation of state. 2006. {\it Ind. Eng. Chem. Res.}, {\bf 45}, 5489 (Invited).

Siderius, D.~W., and Corti, D.~S. Extension of scaled particle theory to inhomogeneous hard particle fluids. II. Theory and simulation of fluid structure surrounding a cavity that intersects a hard wall. 2005. {\it Phys. Rev. E}, {\bf 71}, 036142.

Siderius, D.~W. and Corti, D.~S. Extension of scaled particle theory to inhomogeneous hard particle fluids. I. Cavity growth at a hard wall. 2005. {\it Phys. Rev. E}, {\bf 71}, 036141.
